### 2018-11-21 Sections/physical_architectures_for_quantum_computing.tex
Touch up cross-kerr

In Sec.~\ref{sec:KLM_univ} we showed that with strong cross-Kerr non-linearities\index{cross-Kerr non-linearities} at our disposal, scalable photonic quantum computing is possible. However, the interaction strengths of such devices available in the lab today are minuscule compared to the full $\pi$ phase-shift required for NS and CNOT gates. In LOQC this problem is circumvented using measurement-induced non-linearities, which are sufficiently strong, but necessarily non-deterministic, requiring substantial overheads to accommodate for gate failure.

More recently, as an alternative to using post-selection to simulate strong optical non-linearities, it was shown that by introducing strong coherent states, the strength of the non-linear interaction can be effectively amplified arbitrarily, allowing even very weak non-linearities to be employed for deterministic entangling gate operations \cite{bib:Munro05}, compensated for by using strong coherent states. Thankfully, strong coherent states are an easy resource to come by nowadays.

In this hybrid linear/non-linear optical architecture, a coherent state is used as a `qubus' (quantum bus)\index{Qubus}, which is entangled with the photonic qubits via weak non-linear interactions, thereby mediating long-range entangling operations. This can provide the sufficient entangling power needed to enable scalable, universal quantum computation.

Let us describe the operation of a parity measurement\index{Parity measurements} device using weak non-linearities. This gate could subsequently be employed as a fusion gate\index{Fusion!Gates} (Sec.~\ref{sec:fusion_gates}) for building cluster states, and is therefore a resource for universal quantum computation. Simple extensions of this design idea easily generalise to other non-trivial operations, such as CNOT gates or QND measurements\index{Quantum non-demolition measurements}.

@@

Applying this operation between a coherent state and a photon-number state implements the transformation, 
\begin{align}
\hat{U}_\mathrm{ck} \ket\alpha \ket{n} = \ket{\alpha e^{i\theta n}} \ket{n}.	
\end{align}
Note that the phase-shift accumulated by the coherent state is proportional to the photon-number in the other mode, thereby entangling the two modes.

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a 2-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards to a phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

Now consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances,
\begin{align}
\ket{\psi_\mathrm{in}} &= \alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V}.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}}\ket\alpha &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

@@

This type of non-local gate lends itself very naturally to distributed, network-based implementation, where the quantum internet is employed to mediate the qubus, potentially over long distances.

>>>>

In Sec.~\ref{sec:KLM_univ} we showed that with strong non-linearities\index{Non-linearities} at our disposal, scalable photonic quantum computing is possible. However, the interaction strengths of such devices available in the lab today are minuscule compared to the full $\pi$ phase-shift required for NS and CNOT gate constructions. In LOQC this problem is circumvented using measurement-induced non-linearities, which while are sufficiently strong, are also necessarily non-deterministic, mandating substantial error correction resource overheads to accommodate gate failure.

More recently, as an alternative to using post-selection to simulate strong optical non-linearities, it was shown that by introducing strong coherent states, the strength of the non-linear interaction can be effectively amplified arbitrarily, allowing even very weak non-linearities to be employed for deterministic entangling gate operations \cite{bib:Munro05}, compensated for using strong coherent states. Thankfully, strong coherent states are an easy resource to come by nowadays.

In this hybrid linear/non-linear optical architecture, a coherent state\index{Coherent states} is used as a `qubus' (quantum bus)\index{Qubus}, which is entangled with photonic qubits via weak non-linear interactions, thereby mediating long-range entangling operations. This can provide the sufficient entangling power needed to enable scalable, universal quantum computation.

Let us describe the operation of a parity measurement\index{Parity measurements} device using weak non-linearities. This gate could subsequently be employed as a fusion gate\index{Fusion!Gates} (Sec.~\ref{sec:fusion_gates}) for building cluster states, and is therefore a resource for universal quantum computation. Simple extensions of this design idea easily extend to other non-trivial operations, such as CNOT gates or QND measurements\index{Quantum non-demolition measurements}.

@@

Applying this operation between a coherent state and a photon-number state implements the transformation, 
\begin{align}
\hat{U}_\mathrm{ck} \ket\alpha \ket{n} = \ket{\alpha e^{i\theta n}} \ket{n}.	
\end{align}
Note that the phase-shift accumulated by the coherent state is proportional to the photon-number in the other mode, thereby entangling the two modes via their shared dependence on $n$.

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a 2-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards an $X$-quadrature measurement outcome to a local phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

Consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances, and a coherent state in the qubus mode,
\begin{align}
\ket{\psi_\mathrm{in}} &= (\alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V})\ket\alpha.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}}\ket\alpha &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

@@

This type of non-local gate lends itself very naturally to distributed, network-based implementation, where the quantum internet is employed to mediate the qubus, potentially over long distances. Note that unlike LOQC fusion gates, this gate is non-destructive, and does not require measuring any photonic qubits, only the qubus.
